---
title: "A very silly word cloud project"
author: "Wenshuo Zhang"
date: "April 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Starting code
library(tm) #text mining
library(SnowballC) #stemmers
library(wordcloud) #what it says on the tin
library(readtext) #for reading text files


#this is where the project lives. Despite a very terse academic writing style, my personal life is
#much more haphazard. I also converted all back slashes to forward slashes.

setwd("C:/Users/Natalia/Desktop/Dissertation/zhang dissertation whole 12012017/R project for fun and profit")

```

## R Markdown
This is cribbed almost entirely from https://datascienceplus.com/building-wordclouds-in-r/
Because I wrote a cognitive psychology dissertation (more or less), the prose, especially Chapter 1,
was highly uncharacteristic. Therefore, I wanted to find out what I sounded like


```{r dissertation}

#basic house keeping, read in, get basic info, find out Encoding Info
dissertation <- readtext("zhang_dissertation_final.docx")
typeof(dissertation) #found out that this is a list
head(dissertation)
Encoding(dissertation$text) #UTF-8, because Turkish diacritics are hilarious
```
##Procedure
1. Simplify the data
2. Process the hell out of it

```{r text clean up}
#VectorSource from tm serves up text from a vector
#apparently Corpus needs this?

dissert.text <- Corpus(VectorSource(dissertation$text))

#convert corpus to LC

dissert.text <- tm_map(dissert.text, content_transformer(tolower))

#remove punctuations and stop words
#stop words are commonly used words in the English language.

dissert.text <- tm_map(dissert.text, removePunctuation)
dissert.text <- tm_map(dissert.text, PlainTextDocument)
dissert.text <- tm_map(dissert.text, removeWords, stopwords('english'))

#take only word stems. I hope this is done correctly!

#dissert.text <- tm_map(dissert.text, stemDocument)

```

##Recap

Well, that was fun after a little hiccup. Now I'm going to produce a word cloud, apparently as a graphic!

```{r production}

wordcloud(dissert.text, max.words = 100, random.order = FALSE)
```
